---
title: "ggplot_hook"
author: "Nasri"
date: "2024-09-10"
output:
  pdf_document: default
  html_document: default
---

## Setting up my environment

Notes: setting up my R environtment by loading the 'tidyverse' and 'palmerpenguins' packages

```{r loading packages, warning=FALSE}
library(tidyverse)
library(palmerpenguins)
```

## Visualizations

Here we will go through a series of visualizations

### Flipper and Body mass in purple

Here, we plot flipper length against body mass

```{r }
ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(color="purple")
```

### Flipper and Body mass by species

Here, we plot flipper length against body mass and look at the breakdown by species

```{r}
ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(aes(shape=species))
```

### Flipper and Body mass by species and sex

Here, we plot flipper length against body mass and look at the breakdown by species and sex

```{r}
ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(aes(color=species,
                 shape=species)) +
  facet_wrap(~sex)
```

```{r}
penguins %>%
  drop_na(sex) %>%
  ggplot(aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(aes(color=species,
                 shape=species)) +
  facet_wrap(~sex)
```
